An Algebraic Theory of File Synchronization

### 2015-12-26 2015/axioms.tex
More improvements
Moved more definitions, clarifications

Let us also define the following relations between nodes:

\begin{mydef}[$n\descendant m$]
The partial ordering determined by the parent relation is denoted by $\descendant$:
we write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$),
that is, the path name of $n$ is an initial segment of that of $m$. 
We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
\end{mydef}

\begin{mydef}[$n\unrel m$]
We write $n\unrel m$, or ``$n$ and $m$ are incomparable'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
incomparable nodes are on different branches or on different trees;
none of the path names describing their location is an initial segment of the other.
\end{mydef}

@@

It is intentional that we use the same symbol for independent commands
and sequences as for incomparable nodes. As we will in the next
\namecref{incomparable_is_independent},
these two concepts are closely related.

>>>>

@@

It is intentional that we use the same symbol for independent commands
and sequences as for incomparable nodes. As we will see in the next
\namecref{incomparable_is_independent},
these two concepts are closely related.

### 2015-12-26 2015/comparisons.tex
Moved more definitions, clarifications

It can be easily seen that not all conflicts detected based on the above definition
entails a conflict based on our system; that is, \cite{BP} describes a more
conservative policy.
For example, if $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
the two replicas are derived in the following way:
\begin{gather*}
\FS_A = \cfba{n} \cc \cdba{\nn} \aFS \\
\FS_B = \cfba{n} \aFS,
\end{gather*}
then $\nn$ is dirty in both replicas:
in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
and therefore a conflict is detected at $\nn$.
Our reconciliation algorithm detects no conflicts;
instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
and desired.

>>>>

Similarly to \cite{NREC},
it can be easily seen that not all conflicts detected based on the above definition
entails a conflict based on our system; that is, \cite{BP} describes a more
conservative policy.
For example, if $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
the two replicas are derived in the following way:
\begin{gather*}
\FS_A = \cfba{n} \cc \cdba{\nn} \aFS \\
\FS_B = \cfba{n} \aFS,
\end{gather*}
then $\nn$ is dirty in both replicas:
in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
and therefore a conflict is detected at $\nn$.
Our reconciliation algorithm detects no conflicts;
instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
and desired.

### 2015-12-26 2015/def-filesystem.tex
Moved more definitions, clarifications

The nodes form a disjoint union of rooted directed trees,
which determines the following $\parent$ function.
Tao et al. in \cite{TSR} describe a similar filesystem model, although
they also model inodes and restrict the filesystem to a just single tree.
\begin{mydef}[$\parent$]
The function $\parent(n)$ returns the parent node of $n$, or
returns $\topnode$ if $n$ is the root of a tree.
\end{mydef}

>>>>

The nodes form a disjoint union of rooted directed trees,
which determines the following $\parent$ function,
and \emph{ancestor / descendant} and \emph{incomparable} relations.
Tao et al. in \cite{TSR} describe a similar filesystem model, although
they also model inodes and restrict the filesystem to a just single tree.
\begin{mydef}[$\parent$]
The function $\parent(n)$ returns the parent node of $n$, or
returns $\topnode$ if $n$ is the root of a tree.
\end{mydef}

\begin{mydef}[$n\descendant m$]
On $\setn$ the \emph{ancestor / descendant} relation is the
partial ordering determined by the $\parent$ function.
We write $n\descendant m$ if $n$ is the ancestor of $m$,
that is, $n=\parent^n(m)$ for some integer $n\ge 1$.
% or the path name of $n$ is an initial segment of that of $m$. 
We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
\end{mydef}

\begin{mydef}[$n\unrel m$]
We write $n\unrel m$, or $n$ and $m$ are \emph{incomparable}
if $n\not\descendantEq m$ and $n\not\ancestorEq m$;
that is, incomparable nodes are on different branches or on different trees.
% none of the path names describing their location is an initial segment of the other.
\end{mydef}

### 2015-12-26 2015/works-inverse.tex
Moved more definitions, clarifications

\begin{mylem}\label{worksinputmatch}
If $A$ and $B$ are minimal sequences, $\works{A,B}$,
and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
then their input types must match ($X=Z$).
\end{mylem}
\begin{proof}
This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
either $\cxynv$ or $\czwnv$ would not break, 
and consequently $A$ and $B$ cannot work on the same filesystem.
\end{proof}

@@

From the definitions we can clearly see that
\begin{mycor}\label{negneg_is_typeeq}
$\forall \FS: (S^{-1})^{-1}\aFS\typeeq S\aFS$.
\end{mycor}

>>>>

\begin{mylem}\label{worksinputmatch}
If $A$ and $B$ are minimal sequences, $\works{A,B}$,
and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
then the input types of these commands must match ($X=Z$).
\end{mylem}
\begin{proof}
This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
either $\cxynv$ or $\czwnv$ would not break, 
and consequently $A$ and $B$ cannot work on the same filesystem.
\end{proof}

@@

From the definitions we can clearly see that
\begin{mycor}\label{negneg_is_typeeq}
$\forall S, \FS: (S^{-1})^{-1}\aFS\typeeq S\aFS$.
\end{mycor}
